Density-based [Distributional] State Aggregation \\ in Reinforcement Learning

### 2020-08-20 minutia/icml/workshop.tex
Aggregation paper added

\twocolumn[
\icmltitle{Fast Uniform [Distributional] State Aggregation \\ in Reinforcement Learning}

@@

    Our contribution is a bifurcation.
    We first introduce an algorithm for aggregation in MDPs, then we move on to show advantages of taking such
    aggregation method to work.
    Hereby, we explain the paper structure in brief.
    We first lay down the core concepts of the MDP and the aggregation framework in Sections \ref{sec:mdp} and
    \ref{sec:state-aggregation} then continue to describe the methodology in Section \ref{sec:method}.

@@

    Finding the bin width for a given distribution could be calculated by Freedman-Diaconis rule
    \cite{Freedman1981}.
    As the rule states:

@@

    where n is number of observations and $IQR(x)$ is the inter-quartile range of data.
    This segmentation rule exhibits robustness to sample distribution due to low sensitivity of IQR to outliers and
    heteroscedasticity in the given distribution compared to conventional dispersion measures such as variance or
    standard deviation.
    State values, in this paper, are considered as the similarity metric \textcolor{red}{[measure]} in state
    aggregation.

@@

    For the sake of clarity, we elaborate on some preliminary definitions here to have a consistent set of notations
    to the end of this paper. We use model-free LSPI and LSTDQ \citep{Lagoudakis2003} to update and
    evaluate the policy of actions, respectively.

>>>>

\twocolumn[
\icmltitle{ Density-based [Distributional] State Aggregation \\ in Reinforcement Learning}

@@

    Compared to other kernel-based density estimators such as \citep{HongLim2019}, histograms steer clear of feature
    selection step which is more of an experimental process than a framework of rules to follow.
    Our histogram-based state abstraction model yield a state space model by collecting samples in a domain-agnostic
    way.

    Our contribution is a two-fold.
    We first introduce an algorithm for aggregation in MDPs, then we move on to show advantages of taking such
    aggregation method to work.
    Hereby, we explain the paper structure in brief.
    We first lay down the core concepts of the MDP and the aggregation framework in Sections \ref{sec:mdp} and
    \ref{sec:state-aggregation} then continue to describe the methodology in Section \ref{sec:method}.

@@

    \subsection{Bin width}
    Finding the bin width for a given distribution could be calculated by Freedman-Diaconis's choice
    \cite{Freedman1981}.
    As the rule states:

@@

    where n is number of observations and $IQR(x)$ is the inter-quartile range of data.
    The segmentation rule exhibits robustness to sample distribution due to low sensitivity of IQR to outliers and
    heteroscedasticity in the given distribution compared to conventional dispersion measures such as variance or
    standard deviation.
    State values, in this paper, are considered as the similarity metric \textcolor{red}{[measure]} in state
    aggregation.

@@
